How to \emph{not} write Virtual Machines for Dynamic Languages

### 2007-07-12 talk/dyla2007/dyla.tex
add slang too

PyPy contains a Python interpreter implemented in Python, from which
Python VMs can be generated.  The reader is referred to
\cite{pypyvmconstruction} for a technical presentation.  Let us emphasis
again that the argument we make in the present paper is \emph{not} that
VMs for dynamic languages should be written in their own host language
(as many projects like Squeak \cite{Squeak} and others have done) but
instead that VMs should not be \emph{written} in the first place -- they
should be generated from simple interpreters written in any suitable
high-level language.

>>>>

PyPy contains a Python interpreter implemented in Python, from which
Python VMs can be generated.  The reader is referred to
\cite{pypyvmconstruction} for a technical presentation.  Let us emphasis
again that the argument we make in the present paper is \emph{not} that
VMs for dynamic languages should be written in their own host language
(as many projects like Squeak \cite{Squeak} and others have done) but
instead that VMs should not be \emph{written} in the first place -- they
should be generated from simple interpreters written in any suitable
high-level\footnote{``High-level'' is taken by opposition to languages
like PreScheme \cite{kelsey-prescheme} or the subset of Smalltalk that the
Squeak VM is written in \cite{Squeak} which use the syntax and
metaprogramming facilities of a high-level language but encode
low-level details like memory management.} language.
